---
title: "Report"
author: "Jiaxi Geng"
date: "9/22/2021"
output: html_document
---

## import data set
```{r setup, include=FALSE}
# import raw data set
getwd()
#workingDir <- "."
brinda <- read.csv("brinda12h_psc_jm_Sep2020.csv")
# check the size
dim(brinda)
```
Raw data set has 88607 observations and 225 variables.

## Data cleaning
The inclusion criteria of analysis is sf, crp and agp are not missing. And the imputation process is to substitude zero value of crp and agp with 0.01.
```{r}
# exclude observations with missing value in sf, crp and agp, and get a new data set I am going to focusing on
brindanew <- brinda[!is.na(brinda$sf)&!is.na(brinda$crp)&!is.na(brinda$agp), ]
# set the category according to each limitation
brindanew$category <- NA
brindanew$category[which(brindanew$crp<=5 & brindanew$agp<=1)] <- "Reference"
brindanew$category[which(brindanew$crp>5 & brindanew$agp<=1)] <- "Incubation"
brindanew$category[which(brindanew$crp>5 & brindanew$agp>1)] <- "Early convalescence"
brindanew$category[which(brindanew$crp<=5 & brindanew$agp>1)] <- "Late convalescence"
# imputation of zero value in crp and agp -- change it to 0.01
brindanew$crp[which(brindanew$crp==0)]<-0.01
brindanew$agp[which(brindanew$agp==0)]<-0.01
dim(brindanew)
```
After setting requirements, there there 14068 observations and 225 variables. The new data set is called brindanew.

## do data analysis, get serum ferritin adjusted value with two methods.
```{r}
# install the package
rm(list = ls())
gc()
setwd() # please change the path to the path of BRINDA.R document
if(!("haven" %in% installed.packages()[,"Package"])) {
  install.packages("haven", dependencies = TRUE)
}
library(haven)
source(paste0(getwd(), "/BRINDA.R"))

# Method 1 - overall linear model method
result1 <- BRINDA(dataset = brindanew,
                         retinol_binding_protein_varname = ,
                         retinol_varname = ,
                         ferritin_varname = sf,
                         soluble_transferrin_receptor_varname = , 
                         zinc_varname =,
                         crp_varname = crp, 
                         agp_varname = agp,
                         population = WRA, 
                         crp_ref_value_manual = , 
                         agp_ref_value_manual = , 
                         output_format = simple)
# Method 2 - linear model method for each category
brindanew1 <- brindanew[which(brindanew$category=="Reference"),]
brindanew2 <- brindanew[which(brindanew$category=="Incubation"),]
brindanew3 <- brindanew[which(brindanew$category=="Early convalescence"),]
brindanew4 <- brindanew[which(brindanew$category=="Late convalescence"),]
result2_1 <- BRINDA(dataset = brindanew1,
                         retinol_binding_protein_varname = ,
                         retinol_varname = ,
                         ferritin_varname = sf,
                         soluble_transferrin_receptor_varname = , 
                         zinc_varname =,
                         crp_varname = crp, 
                         agp_varname = agp,
                         population = WRA, 
                         crp_ref_value_manual = , 
                         agp_ref_value_manual = , 
                         output_format = simple)
result2_2 <- BRINDA(dataset = brindanew2,
                           retinol_binding_protein_varname = ,
                           retinol_varname = ,
                           ferritin_varname = sf,
                           soluble_transferrin_receptor_varname = , 
                           zinc_varname =,
                           crp_varname = crp, 
                           agp_varname = agp,
                           population = WRA, 
                           crp_ref_value_manual = , 
                           agp_ref_value_manual = , 
                           output_format = simple)
result2_3 <- BRINDA(dataset = brindanew3,
                           retinol_binding_protein_varname = ,
                           retinol_varname = ,
                           ferritin_varname = sf,
                           soluble_transferrin_receptor_varname = , 
                           zinc_varname =,
                           crp_varname = crp, 
                           agp_varname = agp,
                           population = WRA, 
                           crp_ref_value_manual = , 
                           agp_ref_value_manual = , 
                           output_format = simple)
result2_4 <- BRINDA(dataset = brindanew4,
                           retinol_binding_protein_varname = ,
                           retinol_varname = ,
                           ferritin_varname = sf,
                           soluble_transferrin_receptor_varname = , 
                           zinc_varname =,
                           crp_varname = crp, 
                           agp_varname = agp,
                           population = WRA, 
                           crp_ref_value_manual = , 
                           agp_ref_value_manual = , 
                           output_format = simple)
result2 <- rbind(result2_1,result2_2,result2_3,result2_4)
```
In result data set, sf_adj is the aiming variable that I want to compare.

## Summary tables
Compare the mean sf_adj value for overall data and for each category.
```{r}
library(psych)
library(dplyr)
mean(result1$sf_adj)
result1 %>%
  group_by(category) %>%
  summarise_at(vars(sf_adj), list(name = mean))
mean(result2$sf_adj)
result2 %>%
  group_by(category) %>%
  summarise_at(vars(sf_adj), list(name = mean))
```

## Including plots
Generating boxplot and histogram for each category when comparing between different methods.
```{r pressure, echo=FALSE}
par(mfrow=c(2,2))
boxplot(result1$sf_adj[which(result1$category=="Reference")],main="sf-Method1", xlab="Reference",ylab="Serum ferritin",ylim=c(0,50))
boxplot(result2$sf_adj[which(result2$category=="Reference")],main="sf-Method2", xlab="Reference",ylab="Serum ferritin",ylim=c(0,50))
hist(result1$sf_adj[which(result1$category == "Reference")], prob=TRUE, xlab="Serum ferritin", main="sf-Method1",xlim=c(0,150))
hist(result2$sf_adj[which(result2$category == "Reference")], prob=TRUE, xlab="Serum ferritin", main="sf-Method2",xlim=c(0,150))

boxplot(result1$sf_adj[which(result1$category=="Incubation")],main="sf-Method1", xlab="Incubation",ylab="Serum ferritin",ylim=c(0,50))
boxplot(result2$sf_adj[which(result2$category=="Incubation")],main="sf-Method2", xlab="Incubation",ylab="Serum ferritin",ylim=c(0,50))
hist(result1$sf_adj[which(result1$category == "Incubation")], prob=TRUE, xlab="Serum ferritin", main="sf-Method1",xlim=c(0,150))
hist(result2$sf_adj[which(result2$category == "Incubation")], prob=TRUE, xlab="Serum ferritin", main="sf-Method2",xlim=c(0,150))

boxplot(result1$sf_adj[which(result1$category=="Early convalescence")],main="sf-Method1", xlab="Early convalescence",ylab="Serum ferritin",ylim=c(0,50))
boxplot(result2$sf_adj[which(result2$category=="Early convalescence")],main="sf-Method2", xlab="Early convalescence",ylab="Serum ferritin",ylim=c(0,50))
hist(result1$sf_adj[which(result1$category == "Early convalescence")], prob=TRUE, xlab="Serum ferritin", main="sf-Method1",xlim=c(0,150))
hist(result2$sf_adj[which(result2$category == "Early convalescence")], prob=TRUE, xlab="Serum ferritin", main="sf-Method2",xlim=c(0,150))

boxplot(result1$sf_adj[which(result1$category=="Late convalescence")],main="sf-Method1", xlab="Late convalescence",ylab="Serum ferritin",ylim=c(0,50))
boxplot(result2$sf_adj[which(result2$category=="Late convalescence")],main="sf-Method2", xlab="Late convalescence",ylab="Serum ferritin",ylim=c(0,50))
hist(result1$sf_adj[which(result1$category == "Late convalescence")], prob=TRUE, xlab="Serum ferritin", main="sf-Method1",xlim=c(0,150))
hist(result2$sf_adj[which(result2$category == "Late convalescence")], prob=TRUE, xlab="Serum ferritin", main="sf-Method2",xlim=c(0,150))
```
From the summary information and plots I can draw conclusion that only the Late Convalescence Group has similar results in serum ferritin adjusted values when applying method 1 and method 2 separately, all other groups have very different results. I will try with other methods in the future to see if more accurate and reliable adjusted value can be generated.
